### 2014-04-16 doc/uist14/iteration3.tex
iteration3: remove comment about gender neutral words

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of a user's head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change their location \achal{Should we use gender neutral language?}\bjoern{yes. just did in the previous sentence}. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and orientation sensors on Glass.

>>>>

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of a user's head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change their location. However, as long as the targets are spread around the periphery, their relative orientation doesn't change. This key observation inspires us to investigate a hybrid solution with IR and orientation sensors on Glass.
